Parsing Tweets into Universal Dependencies

### 2017-11-11 paper.tex
add kong and dozat's parsing comparsion and final result.

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank which has 55,607 tokens and it's more than 4 times
larger than the {\sc Tweebank v1}. We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
method achieve an improvement of 2.3 in LAS over the baseline.
\end{abstract}

@@

To conquer the noise in our annotation and achieve better performance
without sacrificing efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show an improvement of more
than 3 points in LAS over baseline parser can be achieved with our
distillation method.

Contribution of this paper includes:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and create a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and dependencies annotation.

\item We built up a whole pipeline to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}). We propose a new distillation
method in training the parser in our pipeline which achieve 3 points improvement
without sacrificing efficiency.
\end{itemize}

@@

\nascomment{I didn't do anything significant to the intro.  for every
  example, make clear whether it's ``real'' or contrived.}

\section{Annotation}\label{sec:anno}

\nascomment{need to introduce this section and explain the structure.}

\subsection{Background: \textsc{Tweebank}}

@@

In some cases, conflicts arose between the UD English 
treebank conventions (UD\_English)
\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
\nascomment{add cite}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

@@

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportion of non-syntactic tokens in the annotation.}\label{tbl:non-synt-prop}
\end{table}
The major characteristic that distinguishes tweets from standard texts is that
there are large proportion of tokens that don't carry any syntactic function.
In our annotation, there are five types of non-syntactic tokens: 
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens.  As discussed above, these are generally
tagged with the \emph{other} (\texttt{X}) part of speech, except
emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the UD
annotation conventions and our guidelines.
Both the guidelines and annotation
were further refined by the authors of this paper to increase
the coverage of our guideline and solve inconsistency between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage (1,041 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. \nascomment{this is
  a little weird:  don't you have to do this before you parse?} Finally, an extra
layer of word-level normalization was manually annotated for data
analysis purposes.

@@

\nascomment{I wonder if we ought to give more detail about our biLSTM
  systems, here and under tokenization?  will reviewers want to know details?}

@@

\paragraph{Final results.}
\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 83.5 & 79.4 \\
		\textsc{distill expert} ($\alpha$=1.0) & 82.2 & 78.0 \\
		\textsc{distill expert} ($\alpha$=0.9) & 82.4 & 78.1 \\		
		\textsc{distill explore} & 82.5 & 78.4 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. \label{tbl:parse-result}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\
		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 94.5 & 92.6 \\
		\textsc{distill expert} ($\alpha$=1.0) & 93.8 & 91.7 \\
		\textsc{distill explore} & 94.1 & 92.0 \\
		\hline
		\newcite{kuncoro-16} & 94.3 & 92.1 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
\end{table}

Our final parsing experiments are shown in Table \ref{tbl:parse-result},
in which we can see that \textsc{distill explore} significant
outperforms \textsc{distill expert}, gaining one more point in LAS improvement.
Additional experiments on the Penn Treebank were performed following
the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
performance close to that of the graph-based parser of \citet{kuncoro-16}.
We attribute the improvements of \textsc{distill explore} over
\textsc{distill expert} to the former's exploration of
ensemble-sanctioned parser states
of different qualities.

\subsection{Final Evaluation}
Finally, we evaluate our full pipeline.

\section{Related Work}

@@

\section{Conclusion}

>>>>

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank which has 55,607 tokens and it's more than 4 times
larger than the {\sc Tweebank v1}. We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.
\end{abstract}

@@

To conquer the noise in our annotation and achieve better performance
without sacrificing efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show an improvement of more
than 2.3 points in LAS over baseline parser can be achieved with our
distillation method and it outperforms other state-of-the-art parsers.

Contribution of this paper includes:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and create a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and dependencies annotation.
We also characterize the difficulties of creating such annotation.

\item We built up a whole pipeline to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}). We propose a new distillation
method in training the parser in our pipeline which achieve 2.3 points improvement
without sacrificing efficiency and outperform other state-of-the-art parsers
in our comparison.
\end{itemize}

@@

\nascomment{I didn't do anything significant to the intro.  for every
  example, make clear whether it's ``real'' or contrived.}
\yjcomment{I've add the source of our example in the figure caption.}
\section{Annotation}\label{sec:anno}

In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
Then we introduce the difference in our part-of-speech (re)annotation with 
\citet{gimpel-EtAl:2011:ACL-HLT2011} which {\sc Tweebank v1} was built 
on (\S\ref{sec:pos-anno}). Then, we move to our efford of adopting the
UD convention to cover tweets specific constructions. At last, we describ
our process of creating new tweet treebank and characterize
the difficulties in reaching consistent annotations.
\nascomment{need to introduce this section and explain the structure.}
\yjcomment{done.}

\subsection{Background: \textsc{Tweebank}}\label{sec:tweebank}

@@

In some cases, conflicts arose between the UD English 
treebank conventions \cite[UD\_English]{Marneffe2014UniversalSD}
\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

@@

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
\end{tabular}
\caption{Proportion of non-syntactic tokens in the annotation.}\label{tbl:non-synt-prop}
\end{table}

The major characteristic that distinguishes tweets from standard texts is that
there are large proportion of tokens that don't carry any syntactic function.
In our annotation, there are five types of non-syntactic tokens: 
sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
these non-syntactic tokens.  As discussed above, these are generally
tagged with the \emph{other} (\texttt{X}) part of speech, except
emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the UD
annotation conventions and our guidelines.
Both the guidelines and annotation
were further refined by the authors of this paper to increase
the coverage of our guideline and solve inconsistency between
different annotators during this exercise. In the second stage, a POS tagger and
parser were trained on the annotated data from the first stage (1,041 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. \nascomment{this is
  a little weird:  don't you have to do this before you parse?}\yjcomment{we were actually correcting the auto-analyzed 2,500 tweets.} Finally, an extra
layer of word-level normalization was manually annotated for data
analysis purposes.

@@

\nascomment{I wonder if we ought to give more detail about our biLSTM
  systems, here and under tokenization?  will reviewers want to know details?}
\yjcomment{I add figure to illustrat our model.}

@@

\paragraph{Final results.}
\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 \\
		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 \\
		\hdashline
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
		Ensemble (20) & 83.5 & 79.4 \\
		\textsc{distill expert} ($\alpha$=1.0) & 82.2 & 78.0 \\
		\textsc{distill expert} ($\alpha$=0.9) & 82.4 & 78.1 \\		
		\textsc{distill explore} & 82.5 & 78.4 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. \label{tbl:parse-result}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{kuncoro-16} & 94.3 & 92.1 \\
		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
		\hdashline
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble (20) & 94.5 & 92.6 \\
		\textsc{distill expert} ($\alpha$=1.0) & 93.8 & 91.7 \\
		\textsc{distill explore} & 94.1 & 92.0 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
\end{table}

Our final parsing experiments are shown in Table \ref{tbl:parse-result}.
We also compare our model with the {\sc TweeboParser} 
of \citet{kong-EtAl:2014:EMNLP2014} and the state-of-the-art parser
 \cite{DBLP:journals/corr/DozatM16} in CoNLL 2017.
Both the compared systems are re-trained on the same data as our system.
From Table \ref{tbl:parse-result}, our baseline system is 1.9 point behind the
state-of-the-art parsing systems. However, through distilling, our baseline
parser catched up and outperform that of \citet{DBLP:journals/corr/DozatM16} and 
\textsc{distill explore} further outperforms \textsc{distill expert}, gaining 0.4
point in LAS improvement. We attribute the improvements of \textsc{distill explore} over
\textsc{distill expert} to the former's exploration of 
ensemble-sanctioned parser states of different qualities.

We also perform additional experiments on the Penn Treebank were performed following
the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
performance close to that of the graph-based parser of \citet{kuncoro-16}.
However, our model is still way behind \citet{DBLP:journals/corr/DozatM16}.
We address this to the intrastic differences between transition-based and graph-based
parsing algorithm.

\subsection{Final Evaluation}
\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it Pipeline & F-score \\
		\hline
		Tokenization & 98.3 \\		
		POS tagging & 93.7 \\
		Dependencies & 74.1 \\
		\hline
	\end{tabular}
	\caption{Evaluating our model in pipeline manner.}\label{tbl:pipline}
\end{table}

Finally, we evaluate the problem of parsing tweets into UD in a pipeline manner.
The results are shown in Table \ref{tbl:pipline}. From this result, we can see
that in the whole pipeline, every component plays an important role. Without
gold segmentation, the parsing performance drops more than 4 points.

%\section{Related Work}

@@

\section{Conclusion}
In this paper, we study the problem of parsing tweets into universal dependencies.
We adopt the UD guidelines to cover 
special constructions in tweets and create
the {\sc Tweebank v2} which has 55,607 tokens. We characterize the disagreements
among our annotations and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. On this new treebank,
we build a pipeline system to parse tweets into UD. We 
propose a new method to distill an ensemble of 20 parsers into a single one
to conquer the annotation noise without sacrificing efficiency.
Our parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.
